sims

### 2024-12-13 manuscript/manuscript.Rmd
update sims and ms

(ref:descr-plot3-caption) Discrete-time hazard and conditional accuracy functions. Discrete time-to-event and conditional accuracy data were simulated for 2000 trials for each of two priming conditions (congruent and incongruent prime stimuli). Error bars represent +/- 1 standard error of the respective proportion. Bin width equals 100 ms.

>>>>

(ref:descr-plot3-caption) Discrete-time hazard and conditional accuracy functions. Discrete time-to-event and conditional accuracy data were simulated for 1000 trials for each of two priming conditions (congruent and incongruent prime stimuli). Error bars represent +/- 1 standard error of the respective proportion. Bin width equals 100 ms.

### 2024-12-13 manuscript/manuscript.tex
update sims and ms

\caption{Discrete-time hazard and conditional accuracy functions. Discrete time-to-event and conditional accuracy data were simulated for 2000 trials for each of two priming conditions (congruent and incongruent prime stimuli). Error bars represent +/- 1 standard error of the respective proportion. Bin width equals 100 ms.}\label{fig:plot3}
\end{figure}

>>>>

\caption{Discrete-time hazard and conditional accuracy functions. Discrete time-to-event and conditional accuracy data were simulated for 1000 trials for each of two priming conditions (congruent and incongruent prime stimuli). Error bars represent +/- 1 standard error of the respective proportion. Bin width equals 100 ms.}\label{fig:plot3}
\end{figure}

### 2024-12-13 sims/sims.Rmd
update sims and ms

This file simulates the data used in Figure 1 of the manuscript and then creates some plots.

@@

```{r}
p_haz_inset_facet <- p8.1b +
  geom_plot(data = inset_facet,
            vp.width = 1/3,
            aes(x, y, label = plot))
p_haz_inset_facet

@@

# Section 11: Simulate hazard data for 1 subject, 1 condition, 200 trials, and plot empirical hazard and survivor functions with error bars (Figure 2)

@@

## hazard

### generate data set

@@

## apply function sim_haz
data_single2 <- sim_haz(subj_n = 1, rep_n = 1000) %>%
               mutate(period = bin,
                      trial = as.integer(str_sub(rep, start=4, end=7)),
                      condition = factor(condition, labels=c("congruent","incongruent"))) %>%
               select(-c("contrast","cumsum","outcomel","outcomen","bin","rep"))  %>%
               mutate(acc = ifelse(period<6 & condition=="incongruent",0,1),
                      acc = ifelse(period==6 & condition=="incongruent" & trial < 500,0,acc)) 
head(data_single2, n=20)
summary(data_single2)

### set up life table

@@

## add ca(t)

@@

### plot hazard functions

@@

## accuracy

```{r}
acc <- tibble(
  time = seq(1,10,1),
  congruent = rep(1,length = 10),
  incongruent = c(0, 0, 0, 0, 0, .5, 1, 1, 1, 1)
) %>% 
  pivot_longer(-time,
               names_to = "condition",
               values_to = "accuracy") %>% 
  mutate(condition = factor(condition))
head(acc,n=20)
```

@@

Combine plots

>>>>

This file simulates the data used in Figures 1, 2, and 3 of the manuscript and then creates some plots.

@@

```{r figure-1}
p_haz_inset_facet <- p8.1b +
  geom_plot(data = inset_facet,
            vp.width = 1/3,
            aes(x, y, label = plot))
p_haz_inset_facet

@@

# Section 11 (Figure 2): Simulate hazard data for 1 subject, 1 condition, 200 trials, and plot empirical hazard and survivor functions with error bars

@@

## generate data set

@@

## apply function sim_haz
ntrials <- 1000

data_single2 <- sim_haz(subj_n = 1, rep_n = ntrials) %>%
               mutate(period = bin,
                      trial = as.integer(str_sub(rep, start=4, end=7)),
                      condition = factor(condition, labels=c("congruent","incongruent"))) %>%
               select(-c("contrast","cumsum","outcomel","outcomen","bin","rep"))  %>%
               mutate(acc = ifelse(period<6 & condition=="incongruent",0,1),
                      acc = ifelse(period==6 & condition=="incongruent" & trial < ntrials/2,0,acc)) 
head(data_single2, n=20)
summary(data_single2)
```

@@

## get ca(t)

@@

## plot hazard functions

@@

## plot ca

@@

## Combine plots
